### 2018-08-08 atomic-swaps/atomic-swaps-paper/intro.tex
[atomic swaps] more explanation about the table

%Their next goal: atomically swap any token for any other token, regardless of the blockchain it resides on.
Ethereum’s Raiden Network is analogous to Bitcoin’s Lightning Network and it provides instant, low-fee and scalable exchanges~\cite{Raiden}. The atomic swap of ERC20 tokens are performed on Raiden network.%Problem in decentralised exchanges: sacrificing transaction speed for settlement on-chain.
Zhang et al. propose Republic Protocol, which is a decentralized open-source dark pool protocol that provides atomic swaps of cryptocurrencies across Bitcoin and Ethereum blockchains~\cite{zhang2017republic}.%Republic: a  facilitating atomic swaps between cryptocurrency pairs across the . Trades are on a hidden orderbook and the matching is done using secure multiparty computation. It is a secure, decentralized, scalable dark pool protocol capable of handling billions in trading volume daily.
Their proposed system enables the exchange of Ether, ERC20 and Bitcoin over a decentralized dark pool. %execution without exposing price and volume, no trusted intermediary to operate a dark pool (dark pool = private exchanges where financial assets and instruments are traded and matched by an engine running on a hidden order book)Republic Protocol removes the risk of asset theft, confiscation or possibility of interference from a malicious exchange operator. Components: Decentralized hidden order book, Decentralized order matching, Atomic swap infrastructure, REN token nodes have no incentive to ignore an order, especially since they do not know the identity of the trader, nor the details of the order
In an atomic cross-chain swap setting, involving parties perform exchange across different blockchains like exchanging Bitcoin for Ether. In ~\cite{herlihy2018atomic}, a cross-chain swap is modeled as a directed graph where vertices correspond to the parties in the protocol and the arcs represent the transfers between them.
%An atomic swap protocol can be thought of as a trust-free, Byzantine-hardened form of distributed commitment. An atomic cross-chain swap is a special case of a distributed atomic transaction, although not all atomic transactions can be expressed as cross-chain swaps. If swaps are recurrent, then it would be useful to conduct swaps off-chain as much as possible, similar to the way that Lightning and Raiden networks support off-chain transactions for bitcoin and ERC20 tokens.

%FAIR EXCHANGE?
%The fair exchange problem ~\cite{franklin1998secure}, ~\cite{micali2003simple} is a precursor to the atomic cross-chain swap problem. Alice has a digital asset Bob wants, and vice-versa, and at the end of the protocol, either Alice and Bob have exchanged assets, or they both keep their assets. In the absence of blockchains, trusted, or semi-trusted third parties are required, but roles of those trusted parties can be minimized in clever ways.

@@

\begin{table}[h!]
\footnotesize
\centering
%\Huge
%\resizebox{\columnwidth}{!}{%
\begin{tabular}{ |c|c|c|c|c|c| }
  \hline
   maker & taker & class & order transactions (margin) & account (onetime) transactions (fixed) \\ \hline
   ERC20 & ETH & approve & 3 & \\ \hline
   ERC20 & ERC20 & approve & 4 & \\ \hline
   ERC20-like & ETH & w/o approve & 5 & \\ \hline
   ERC20-like & ERC20-like & w/o approve & 6 & \\ \hline
   ERC223 & ETH & & &\\ \hline
   ERC20 & ETH & collateralized & &\\ \hline
   ERC20 & ETH & partially collateralized & &\\ \hline
\end{tabular}
\caption {swaps}
%}
\end{table}\label{Table:Comparison of different swaps}

>>>>

%https://medium.com/@bitcoinatom/why-are-atomic-swaps-better-than-trading-on-exchanges-798492e150fd
%Their next goal: atomically swap any token for any other token, regardless of the blockchain it resides on.
Ethereum’s Raiden Network is analogous to Bitcoin’s Lightning Network and it provides instant, low-fee and scalable exchanges~\cite{Raiden}. The atomic swap of ERC20 tokens are performed on Raiden network.%Problem in decentralised exchanges: sacrificing transaction speed for settlement on-chain.
Zhang et al. propose Republic Protocol, which is a decentralized open-source dark pool protocol that provides atomic swaps of cryptocurrencies across Bitcoin and Ethereum blockchains~\cite{zhang2017republic}.%Republic: a  facilitating atomic swaps between cryptocurrency pairs across the . Trades are on a hidden orderbook and the matching is done using secure multiparty computation. It is a secure, decentralized, scalable dark pool protocol capable of handling billions in trading volume daily.
Their proposed system enables the exchange of Ether, ERC20 and Bitcoin over a decentralized dark pool. %execution without exposing price and volume, no trusted intermediary to operate a dark pool (dark pool = private exchanges where financial assets and instruments are traded and matched by an engine running on a hidden order book)Republic Protocol removes the risk of asset theft, confiscation or possibility of interference from a malicious exchange operator. Components: Decentralized hidden order book, Decentralized order matching, Atomic swap infrastructure, REN token nodes have no incentive to ignore an order, especially since they do not know the identity of the trader, nor the details of the order
In an atomic cross-chain swap setting, involving parties perform exchange across different blockchains like exchanging Bitcoin for Ether. In ~\cite{herlihy2018atomic}, a cross-chain swap is modeled as a directed graph where vertices correspond to the parties in the protocol and the arcs represent the transfers between them.
%An atomic swap protocol can be thought of as a trust-free, Byzantine-hardened form of distributed commitment. An atomic cross-chain swap is a special case of a distributed atomic transaction, although not all atomic transactions can be expressed as cross-chain swaps. If swaps are recurrent, then it would be useful to conduct swaps off-chain as much as possible, similar to the way that Lightning and Raiden networks support off-chain transactions for bitcoin and ERC20 tokens.FAIR EXCHANGE? The fair exchange problem ~\cite{franklin1998secure}, ~\cite{micali2003simple} is a precursor to the atomic cross-chain swap problem. Alice has a digital asset Bob wants, and vice-versa, and at the end of the protocol, either Alice and Bob have exchanged assets, or they both keep their assets. In the absence of blockchains, trusted, or semi-trusted third parties are required, but roles of those trusted parties can be minimized in clever ways.

@@

\section{Atomic swaps with different settings}

\begin{table}[h!]
\footnotesize
\centering
%\Huge
%\resizebox{\columnwidth}{!}{%
\begin{tabular}{ |c|c|c|c|c|c| }
  \hline
   maker & taker & class & order transactions (margin) & account (onetime) transactions (fixed) \\ \hline
   ERC20 & ETH & approve & 2 & 3 \\ \hline
   ERC20 & ERC20 & approve & 3 & 4 \\ \hline
   ERC20-like & ETH & w/o approve &  & \\ \hline
   ERC20-like & ERC20-like & w/o approve &  & \\ \hline
   ERC223 & ETH & & &\\ \hline
   ERC20 & ETH & collateralized & &\\ \hline
   ERC20 & ETH & partially collateralized & &\\ \hline
   ERC20 & ERC223 & & \\ \hline
\end{tabular}
\caption {swaps}
%}
\end{table}\label{Table:Comparison of different swaps}
\textbf{ERC20 to ETH:} Somebody sets up the swap. Token holder calls approve on the ERC20 contract with the swap contract as the target/allowance holder/spender. The holder of the ETH calls a settle function, sending their ETH along with it. This triggers the swap and the swap contract calls transferFrom on the ERC20 contract, transferring the tokens from the token holder to the ETH holder. The swap contract at this stage also sends the ETH to the token holder. The atomic swap is now complete. Hence, approving on the ERC20 contract and calling the settle function are counted as the order transactions. When the one-time transactions are also considered, deploying the swap contract should also be counted, which in total makes 4 transactions. We assume that the token contract already exists.

\textbf{ERC20 to ERC20:} For the order transactions, we have 3 in total as the other token holder should also approve the amount of tokens to be spent.
